Neural Power Units

### 2020-06-02 papers/main.tex
pdflatex

\begin{table}[h]
  \centering
  \caption{Model definitions for the simple arithmetic task}
  \label{tab:models_simple_task}
  \begin{tabular}{llll}
    \toprule
    Model & Layer 1 & Layer 2 & Layer 3 \\
    \midrule
    NPU & NAU(2,\,6) & NPU(6,\,2) & -- \\
    NMU & NAU(2,\,6) & NMU(6,\,2) & -- \\
    NALU & NALU(2,\,6) & NALU(6,\,2) & -- \\
    iNALU & iNALU(2,\,6) & iNALU(6,\,2) & -- \\
    Dense & Dense(2,\,10,\,\sigma) & Dense(10,\,10,\,\sigma) & Dense(10,\,2) \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\begin{table}[h]
  \centering
  \caption{Model definitions for the simple arithmetic task}
  \label{tab:models_simple_task}
  \begin{tabular}{llll}
    \toprule
    Model & Layer 1 & Layer 2 & Layer 3 \\
    \midrule
    NPU & NAU(2,\,6) & NPU(6,\,2) & -- \\
    NMU & NAU(2,\,6) & NMU(6,\,2) & -- \\
    NALU & NALU(2,\,6) & NALU(6,\,2) & -- \\
    iNALU & iNALU(2,\,6) & iNALU(6,\,2) & -- \\
    Dense & Dense(2,\,10,\,$\sigma$) & Dense(10,\,10,\,$\sigma$) & Dense(10,\,2) \\
    \bottomrule
  \end{tabular}
\end{table}
